From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-01 Pi+/paper/finite.tex
More text

Instead, in the proof, we will think about the free group as it was introduced at the beginning: elements of the free group as words over an alphabet of letters from generating set and the set of their formal inverses. If we take the disjoint union of $A$ with itself, that is, $A + A$ as the group's underlying set, we can use $\inl/\inr$ to mark the elements - for example, by stating that $\inl(a)}$ means $a$ and $\inr(a)$ means $\inv{a}$. 
Hence, we can encode the free group using the free monoid - which is to say, lists on $A + A$. Additionally, we need to ensure that group laws hold, so words identified by the group equations are equalt. Thus, elements of the group will actually be equivalence classes of lists on $A + A$.

>>>>

Instead, in the proof, we will think about the free group as it was introduced at the beginning: elements of the free group as words over an alphabet of letters from generating set and the set of their formal inverses. If we take the disjoint union of $A$ with itself, that is, $A + A$ as the group's underlying set, we can use $\inl/\inr$ to mark the elements - for example, by stating that $\inl{a}$ means $a$ and $\inr{a}$ means $\inv{a}$. 
Hence, we can encode the free group using the free monoid - which is to say, lists on $A + A$. Additionally, we need to ensure that group laws hold, so words identified by the group equations are equalt. Thus, elements of the group will actually be equivalence classes of lists on $A + A$.
